\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
add ref to image in weights

\begin{abstract}
Understanding how the brain works is a key
to treat brain disorders such as Parkinson's disease,
epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
light on the anatomical and functional connectivity of the brain. In the
context of the Connectomics challenge, we propose a simple  algorithm made of
four stages, using preprocessing and partial correlation to achieve a network
inference of high quality. We put in perspective our method
with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
(\cite{huynhthu2010inferring}).

@@

\textcolor{red}{By nature, the firing event is really fast and in order to 
retrieve the connectivity from them, it is necessary to link a burst to a 
couple of timesteps (ideally one). The small decay for the fluorescent calcium 
indicator implies a signal variation during a long interval and therefore, in 
order to only keep rising and strong transitions, we apply a hard-tresholing filter: 
$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ 
As a result, we get a binary-like signal with the true activity when a burst 
happens and with a true zero when the neuron is inactive.}

@@

\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the 
current activity of the systems in order to favor the association measure inversely 
proportional to the number of neurons firing together:
$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $. 
When too much neurons are firing together, i.e. a network burst, it is almost 
impossible to retrieve direct relationships: all neurons seem to be directly 
connected to each other. By favoring the association measure when the activity is low, 
we expect to retrieve a pair of neurons that are really directly connected together. 
}

>>>>

\begin{abstract}
Understanding how the brain works is a key
to treat brain disorders such as Parkinson's disease,
epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
light on the anatomical and functional connectivity of the brain. In the
context of the Connectomics challenge, we propose a simple algorithm made of
four stages, using preprocessing and partial correlation to achieve a network
inference of high quality. An optimized variation of this simple algorithm 
is the winning method of the Connectomics Challenge.

We put in perspective our method
with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
(\cite{huynhthu2010inferring}).

@@

\textcolor{red}{By nature, the firing event is really fast and in order to 
retrieve the connectivity from them, it is necessary to link a burst to a 
couple of timesteps (ideally one). The small decay for the fluorescent calcium 
indicator implies a signal variation during a long interval and therefore, in 
order to only keep rising and strong transitions, we apply a hard-tresholing filter: 
$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ where $\tau$ is a given threshold.
As a result, we get a binary-like signal with the true activity when a burst 
happens and with a true zero when the neuron is inactive.}

@@

\textcolor{red}{Then we apply on the entire signal a non-linear filter based on the 
current activity of the systems in order to favor the association measure inversely 
proportional to the number of neurons firing together:
$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $. 
When too much neurons are firing together, i.e. in case of a network burst, it is almost 
impossible to retrieve direct relationships: all neurons seem to be directly 
connected to each other. By favoring the association measure when the activity is low, 
we expect to retrieve a pair of neurons that are really directly connected together. 
In concrete terms, as it can be verified on \textit{fig 1}, peak intensity may change in function 
of the activity of all neurons but the number and the locations of peaks is not modified.
}
